Doppler Imaging Fun

### 2019-07-03 tex/gitlinks.tex
nothin

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/40d52a59e985547aaf7d10e12ac20e4c2247ac4d/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/40d52a59e985547aaf7d10e12ac20e4c2247ac4d/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/40d52a59e985547aaf7d10e12ac20e4c2247ac4d/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

>>>>

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/91e40d1f56ca84e6a02a7a8d0a650deefdd735aa/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/91e40d1f56ca84e6a02a7a8d0a650deefdd735aa/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/91e40d1f56ca84e6a02a7a8d0a650deefdd735aa/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
